---
title: "Faithful data exploration"
author: "Mubarak Mojoyinola"
date: "2024-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
```

## 1. Average Waiting Time Between Eruptions
```{r}
data <- faithful
```

The average waiting time between eruptions of the __Old Faithful__ geyser in the data set `faithful` is `r round( mean(data$waiting), 2)` minutes.

## 2. First Four Eruption Durations
Below is the duration of the first four eruptions in  minutes.

```{r}
knitr::kable(head(data$eruptions, n = 4),col.names = "Duration(min)")
```

## 3. First Five Records of the Eruptions Data

The first five rows of the data set `faithful` is displayed below. 
```{r, echo = FALSE}
d <-head(data, n =5)
kbl <- knitr::kable(d, format = "html")
kableExtra::kable_styling(kbl, full_width = FALSE)
```

## 4. Histogram of Eruption Durations

```{r}
hist(data$eruptions, main = "Histogram of Eruption Durations",
     xlab = "Eruption duration (min)")
```

The figure above indicates a bimodal distribution of eruption durations. One group exhibits eruptions lasting less than 3 minutes, while the other group had eruptions lasting from more than 3 minutes up to 5 minutes.